When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-06-15 06_Paper/COG-ED/Stage 2/Supplement.Rmd
put explor1 figure in supplement

>>>>

```{r nfcgroups-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median. $N=116$. The scatter has a horizontal jitter of 0.2. Smoothing of conditional means with Loess method. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "nfcgroups-sv.png"))
